---
title: "Conley Standard Errors in R"
author: "Nicholas Potter"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette documents the history and use of this package, which is essentially just a repackaging of code from a series of previous efforts. Conley standard errors account for spatial correlation and are a good alternative in a fixed-effects model when spatial clusters may be too big or too small, as is often the case when using climate data that does not conform to administrative boundaries.

## Usage

Usage is similar to the use of variance-covariance matrices from the package `sandwhich`:

```{r echo=TRUE}
library(ConleySE)
library(lmtest)
library(sandwich)
data(conley_spatial)

# For cross-sectional data, limit to one year:
cs2012 <- conley_spatial[conley_spatial$year == 2012,]
m1 <- lm(EmpClean00 ~ HDD + CDD, data = cs2012)

vcov_spatial <- vcovConley(model = m1,
               x = cs2012$longitude,
               y = cs2012$latitude,
               dist_fn = "SH", dist_cutoff = 500, 
               verbose = FALSE) 

coeftest(m1) #OLS
coeftest(m1, vcov = vcovHC(m1, type = "HC1")) # Robust standard errors as in Stata
coeftest(m1, vcov = vcov_spatial) #Spatial SEs
```


