---
title: "Conley Standard Errors in R"
author: "Nicholas Potter"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette documents the history and use of this package, which is essentially just a repackaging of code from a series of previous efforts. Conley standard errors account for spatial correlation and are a good alternative in a fixed-effects model when spatial clusters may be too big or too small, as is often the case when using climate data that does not conform to administrative boundaries.

## Usage

Usage is similar to the use of variance-covariance matrices from the package `sandwhich`:

```{r echo=TRUE}
library(ConleySE)
library(lmtest)
library(sandwich)
data(conley_spatial)

# For cross-sectional data, limit to one year:
cs2012 <- conley_spatial[conley_spatial$year == 2012,]
m1 <- lm(EmpClean00 ~ HDD + CDD, data = cs2012)

vcov_spatial <- ConleySE(model = m1,
               x = cs2012$longitude,
               y = cs2012$latitude,
               dist_fn = "SH", dist_cutoff = 500, 
               verbose = FALSE) 

coeftest(m1) #OLS
coeftest(m1, vcov = vcovHC(m1, type = "HC1")) # Robust standard errors as in Stata
coeftest(m1, vcov = vcov_spatial) #Spatial SEs
```




Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
